\rhead{\bf MC\_QueueXXLock()}
\noindent
\vspace{5pt}
\rule{6.5in}{0.015in}
\noindent
{\LARGE \bf MC\_QueueRDLock()\index{MC\_QueueRDLock()}}\\
{\LARGE \bf MC\_QueueWRLock()\index{MC\_QueueWRLock()}}\\
{\LARGE \bf MC\_QueueRDUnlock()\index{MC\_QueueRDUnlock()}}\\
{\LARGE \bf MC\_QueueWRUnlock()\index{MC\_QueueWRUnlock()}}\\
\phantomsection
\addcontentsline{toc}{section}{MC\_QueueXXLock()}

\noindent
{\bf Synopsis}\\
{\bf \#include $<$libmc.h$>$}\\
{\bf int MC\_QueueXXLock}({\bf MCAgency\_t} $agency$, {\bf MC\_QueueIndex\_e} $queue$);\\

\noindent
{\bf Purpose}\\
These functions lock a Mobile-C data queue for reading or writing.

\noindent
{\bf Return Value}\\
The function returns 0 on success and non-zero otherwise.\\

\noindent
{\bf Parameters}
\vspace{-0.1in}
\begin{description}
\item               
\begin{tabular}{p{10 mm}p{145 mm}}
$agency$ & A handle associated with a running agency. \\
$queue$ & An enumerated value specifying which queue to lock or unlock.
\end{tabular}
\end{description}

\noindent
{\bf Description}\\
This function locks a queue for reading and writing. The enumerated values
for the queue are:


\begin{tabular}{p{50 mm}p{110 mm}}
\hline
Macro & Description \\
\hline
{\texttt enum MC\_QueueIndex\_e} & \\
\hline
\texttt{MC\_QUEUE\_MESSAGE} \index{MC\_QUEUE\_MESSAGE} & The message queue. \\
\texttt{MC\_QUEUE\_AGENT} \index{MC\_QUEUE\_AGENT} & The message queue. \\
\texttt{MC\_QUEUE\_CONNECTION} \index{MC\_QUEUE\_CONNECTION} & The connection queue. \\
\texttt{MC\_QUEUE\_SYNC} \index{MC\_QUEUE\_SYNC} & The synchronization object queue. \\
\texttt{MC\_QUEUE\_BARRIER} \index{MC\_QUEUE\_BARRIER} & The barrier object queue. 
\end{tabular}

The \texttt{MC\_QueueRDLock()} function locks a queue for reading. If a queue
is locked for reading, other threads are still able to read from the queue, but
no thread will be able to lock the queue for writing. If a read lock is
requested on a queue that is currently write-locked, the function will block
until the write-lock is lifted.

The \texttt{MC\_QueueWRLock()} function locks a queue for writing. If other
threads currently have read or write locks on the queue, this function 
will block until all other readers and writers have released their locks.
At this point the function will attain a write lock on the queue, and no
other threads will be able to attain read or write locks until the 
locking thread has unlocked the write-lock.

These functions are useful for suspending certain queues, such as the agent queue,
to make sure they are not modified while user-space algorithms are running. For
instance, if the user wants to retrieve the number of agents currently residing on the
system, and then perform an action on each agent, the user should first place lock the queue
to ensure that no agents are added or deleted from the queue during the middle of operations.

Note that any queue that is locked by the user should also be unlocked by the user with 
the corresponding functions, or the agency will cease to function normally. 

Following is a brief summary of the effects of locking each queue.
\begin{itemize}
\item The message queue: Locking the message queue will prevent Mobile-C from
processing new messages. Connections will still be accepted, but agent
migration message, FIPA-ACL messages, and other types of messages will not be
processed.
\item The agent queue: Locking the agent queue will prevent Mobile-C from
adding or removing agents. For new agents, agent and message processing is
still executed up until the last step where the agent is to be added to the
queue. This might be useful if you are processing agents in an agency and must
ensure that no agents are added or deleted during processing.
\item The connection queue: Locking this will effectively prevent Mobile-C from
processing new connections.
\item The sync queue: Locking this queue for writing will cause all Mobile-C
synchronization functions, such as \texttt{MC\_MutexLock}, to block until the
queue is unlocked. Locking this queue for reading will prevent new
synchronization nodes from being created.
\item The barrier queue: Locking this queue will have similar effects as
locking the sync queue, except for Mobile-C barriers.
\end{itemize}
\noindent
{\bf Example}\\
\noindent
%{\footnotesize\verbatiminput{../demos/getting_started/hello_world/server.c}}

\noindent

%\CPlot::\DataThreeD(), \CPlot::\DataFile(), \CPlot::\Plotting(), \plotxy().\\
